Topological Equivariant Artist Model for Visualization Library Architecture

### 2021-10-07 paper/main.tex
paper

Here we present a very brief summary of topics, for more information see Hatcher\cite{hatcherAlgebraicTopology2002}, Munkres\cite{munkresElementsAlgebraicTopology1984}, and Bradley et. al. \cite{bradleyTopologyCategoricalApproach2020}.

@@

>>>>

Here we present a very brief summary of topics, for more information Hatcher\cite{hatcherAlgebraicTopology2002}, Munkres\cite{munkresElementsAlgebraicTopology1984}, and Spanier \cite{spanier1989algebraic}.

@@

For more information on category theory, see Barr and Wells\cite{barrCategoryTheoryComputing}, Fong and Spivak \cite{fongInvitationAppliedCategory2019}, Riehl\cite{riehlCategoryTheoryContext} and Bradley et. al. \cite{bradleyTopologyCategoricalApproach2020}.
